---
title: "Useful R-Packages"
author: "David Izydorczyk"
date: "Last Updated 01.07.2021"
output:
  html_document:
     keep_md: yes
     toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

This is an internal collection of useful R-packages I found over the time and often have to Google again, if I want to use them.

## Correlations      


The [`correlation`](https://github.com/easystats/correlation) package provides an easy to use way to calculate and print correlation analysis for different types of correlations ()

```{r}
library(correlation)

results <- correlation(mtcars %>% select(mpg,hp,cyl))
results
summary(results)
```


## Model outputs     

The [`parameters`](https://github.com/easystats/parameters)  package provides utilities for processing the parameters of various statistical models:


```{r message=FALSE, warning=FALSE}
library(parameters)
library(lme4)


m <- lmer(weight ~ Diet + (1 + Time | Chick), data = ChickWeight)

model_parameters(m, effects = "all")

```

## Model performance 


The [`performance`](https://github.com/easystats/performance)  package provides utilities for computing and extracting indices of model quality and goodness of fit (e.g., $R^2$, RMSE, ICC, AIC, BIC) for different types of models (`lm`, `glm`, `lmer`):


```{r message=FALSE, warning=FALSE}
library(performance)
library(lme4)

m1 <- lmer(weight ~ 1 + (1 + Time | Chick), data = ChickWeight)
model_performance(m1)

m2 <- lmer(weight ~ Diet + (1 + Time | Chick), data = ChickWeight)


compare_performance(m1, m2, rank = TRUE)
test_bf(m1, m2)
```








## MCMC handling     

The [`MCMCvis`](https://cran.r-project.org/web/packages/MCMCvis/vignettes/MCMCvis.html) package is an R package used to visualize, manipulate, and summarize MCMC output:


```{r message=FALSE, warning=FALSE}
library(MCMCvis)

MCMCsummary(MCMC_data, params = "alpha", round = 2)


means <- c(-10,-10)
prior <- runif(1e4,-100,100)

MCMCtrace(MCMC_data,
          params = c("beta[1]","beta[2]"),
          ISB    = FALSE,
          n.eff  = TRUE,
          Rhat   = TRUE,
          pdf    = FALSE,
          ind    = TRUE,
          gvals  = means,
          priors = prior)
```



## Plots for posters or presentations 

The [`ggstatsplot`](https://github.com/IndrajeetPatil/ggstatsplot) "is an extension of ggplot2 package for creating graphics with details from statistical tests included in the information-rich plots themselves.". I found this useful for preparing plots for (poster) presentations, since they already incleade descriptive and inference statistics.

```{r}
library(ggstatsplot)


ggbetweenstats(
  data     = ChickWeight,
  x        = Diet,
  y        = weight,
  title    = "Distribution of Chicken Weights",
  ggtheme  = theme_bw()
)
```



## Cohens D 

The best package I found to calculate Cohen's d is the [lsr](https://cran.r-project.org/web/packages/lsr/lsr.pdf) package, which provides a "collection of tools intended to make introductory statistics easier to teach, including wrappers for common hypothesis tests and basic data manipulation":


```{r}
library(lsr)

chickwts %>%
  filter(feed == "casein" | feed == "horsebean") %>% 
  mutate(feed = droplevels(feed)) %>% 
  cohensD(weight ~ feed, data = .)

```



